Global code motion of congruent instructions

### 2017-04-18 paper.tex
make last table fit without overflow

\begin{verbatim}
void doGCM()
  Analyses available: Dominator Tree, DFS Numbering, Memory SSA,
  Compute DJ-graph of function and compute mergeset based on that
  do
    Compute GVN of each expression in the function
  while (doCodeHoisting() > 0) // If any of candidates were hoisted then repeat hoisting
  doCodeSinking()
\end{verbatim}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|r|r|r|r|r|r|r|r|r|r|r|r|}
      \hline
  &  \multicolumn{3}{|c|}{Hoisted by LICM} &\multicolumn{3}{|c|}{Sunk by LICM} &\multicolumn{3}{|c|}{Functions Inlined} &  \multicolumn{3}{|c|}{Functions Deleted} \\\hline
 Benchmarks       & Base        & \GCM{}	& \%  &Base     & \GCM{}   &\%    & Base	& \GCM{}	  &\%   & Base	& \GCM{}	& \% \\\hline
 400.perlbench	  & 2428	& 2480	& 2.1 & 36	& 35	& -2.8 & 1562	& 1565	  & 0.2 & 232	& 234	& 0.9  \\\hline
 401.bzip2	  & 721	        & 825	& 14.4& 3	& 3	& 0.0  & 172	& 180	  & 4.7 & 32	& 33	& 3.1  \\\hline
 403.gcc	  & 8867	& 10079	& 13.7& 143	& 182	& 27.3 & 5034	& 5080	  & 0.9 & 1303	& 130	& 0.1  \\\hline
 429.mcf	  & 55	        & 51	& -7.3& 1	& 1	& 0.0  & 4	& 4	  & 0.0 & 0 	& 0	& 0.0  \\\hline
 433.milc	  & 2537	& 2795	& 10.2& 3	& 3	& 0.0  & 75	& 81	  & 8.0 & 0	& 0	& 0.0  \\\hline
 444.namd	  & 2204	& 2206	& 0.1 & 240	& 240	& 0.0  & 387	& 390	  & 0.8 & 57	& 55	& -3.5 \\\hline
 445.gobmk	  & 3090	& 3107	& 0.6 & 18	& 19	& 5.6  & 735	& 775	  & 5.4 & 230	& 234	& 1.7  \\\hline
 447.dealII	  & 59114	& 95884	& 62.2& 60	& 8	& -86.7& 100891& 100692  & -0.2& 30219	& 29966	& -0.8 \\\hline
 450.soplex	  & 4668	& 4848	& 3.9 & 18	& 17	& -5.6 & 9801	& 9784	  & -0.2& 3125	& 3112	& -0.4 \\\hline
 453.povray	  & 9533	& 9079	& -4.8& 23	& 32	& 39.1 & 5522	& 5532	  & 0.2 & 1202	& 1201	& -0.1 \\\hline
 456.hmmer	  & 3200	& 3232	& 1.0 & 3	& 8	& 166.7& 562	& 562	  & 0.0 & 103	& 101	& -1.9 \\\hline
 458.sjeng	  & 400	        & 446	& 11.5& 0	& 0	& 0.0  & 127	& 135	  & 6.3 & 18	& 18	& 0.0  \\\hline
 462.libquantum	  & 362	        & 386	& 6.6 & 0 	& 0	& 0.0  & 87	& 87	  & 0.0 & 21	& 21	& 0.0  \\\hline
 464.h264ref	  & 17075	& 17153	& 0.5 & 4	& 4	& 0.0  & 338	& 382	  & 13.0& 72	& 72	& 0.0  \\\hline
 470.lbm	  & 39	        & 39	& 0.0 & 0	& 0	& 0.0  & 13	& 13	  & 0.0 & 4	& 4	& 0.0  \\\hline
 471.omnetpp	  & 565	        & 661	& 17.0& 32	& 30	& -6.3 & 4790	& 4843	  & 1.1 & 1321	& 1316	& -0.4 \\\hline
 473.astar	  & 691	        & 754	& 9.1 & 0	& 0	& 0.0  & 359	& 363	  & 1.1 & 113	& 113	& 0.0  \\\hline
 482.sphinx3	  & 1599	& 1693	& 5.9 & 11	& 9	& -18.2& 198	& 194	  & -2.0& 53	& 53	& 0.0  \\\hline
 483.xalancbmk	  & 9997	& 11453	& 14.6& 56	& 54	& -3.6 & 69534	& 68839	  & -1.0& 29875	& 29519	& -1.2 \\\hline
    \end{tabular}
  \end{center}
  \caption{Static metrics before (Base) and after \gcm{} (\GCM{}) on
    \SPEC{} at -Ofast. The \% Column show percentage increase in metric
    w.r.t. Base. \GCM{} improves LICM and inlining.}
  \label{tab:stats}
\end{table}

>>>>

\begin{verbatim}
void doGCM()
  Analyses available: Dominator Tree, DFS Numbering, Memory SSA,
  Compute DJ-graph of function and compute mergeset based on that
  do
    Compute GVN of each expression in the function
  while (doCodeHoisting() > 0) // Repeat hoisting if any candidates were hoisted.
  doCodeSinking()
\end{verbatim}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|r|r|r|r|r|r|r|r|r|r|r|r|}
      \hline
  &  \multicolumn{3}{|c|}{Hoisted by LICM} &\multicolumn{3}{|c|}{Sunk by LICM} &\multicolumn{3}{|c|}{Functions Inlined} &  \multicolumn{3}{|c|}{Functions Deleted} \\\hline
 {\Small Bmarks}          & Base        & \GCM{}	& \%  &Base     & \GCM{}   &\%    & Base	& \GCM{}	  &\%   & Base	& \GCM{}	& \% \\\hline
 {\Small 400.perlb}	  & 2428	& 2480	& 2.1 & 36	& 35	& -2.8 & 1562	& 1565	  & 0.2 & 232	& 234	& 0.9  \\\hline
 {\Small 401.bzip2}	  & 721	        & 825	& 14.4& 3	& 3	& 0.0  & 172	& 180	  & 4.7 & 32	& 33	& 3.1  \\\hline
 {\Small 403.gcc}	  & 8867	& 10079	& 13.7& 143	& 182	& 27.3 & 5034	& 5080	  & 0.9 & 1303	& 130	& 0.1  \\\hline
 {\Small 429.mcf}	  & 55	        & 51	& -7.3& 1	& 1	& 0.0  & 4	& 4	  & 0.0 & 0 	& 0	& 0.0  \\\hline
 {\Small 433.milc}	  & 2537	& 2795	& 10.2& 3	& 3	& 0.0  & 75	& 81	  & 8.0 & 0	& 0	& 0.0  \\\hline
 {\Small 444.namd}	  & 2204	& 2206	& 0.1 & 240	& 240	& 0.0  & 387	& 390	  & 0.8 & 57	& 55	& -3.5 \\\hline
 {\Small 445.gobmk}	  & 3090	& 3107	& 0.6 & 18	& 19	& 5.6  & 735	& 775	  & 5.4 & 230	& 234	& 1.7  \\\hline
 {\Small 447.dealII}	  & 59114	& 95884	& 62.2& 60	& 8	& -86.7& 100891& 100692  & -0.2& 30219	& 29966	& -0.8 \\\hline
 {\Small 450.soplex}	  & 4668	& 4848	& 3.9 & 18	& 17	& -5.6 & 9801	& 9784	  & -0.2& 3125	& 3112	& -0.4 \\\hline
 {\Small 453.povray}	  & 9533	& 9079	& -4.8& 23	& 32	& 39.1 & 5522	& 5532	  & 0.2 & 1202	& 1201	& -0.1 \\\hline
 {\Small 456.hmmer}	  & 3200	& 3232	& 1.0 & 3	& 8	& 166.7& 562	& 562	  & 0.0 & 103	& 101	& -1.9 \\\hline
 {\Small 458.sjeng}	  & 400	        & 446	& 11.5& 0	& 0	& 0.0  & 127	& 135	  & 6.3 & 18	& 18	& 0.0  \\\hline
 {\Small 462.libqua}     & 362	        & 386	& 6.6 & 0 	& 0	& 0.0  & 87	& 87	  & 0.0 & 21	& 21	& 0.0  \\\hline
 {\Small 464.h264}	  & 17075	& 17153	& 0.5 & 4	& 4	& 0.0  & 338	& 382	  & 13.0& 72	& 72	& 0.0  \\\hline
 {\Small 470.lbm}	  & 39	        & 39	& 0.0 & 0	& 0	& 0.0  & 13	& 13	  & 0.0 & 4	& 4	& 0.0  \\\hline
 {\Small 471.omnet}	  & 565	        & 661	& 17.0& 32	& 30	& -6.3 & 4790	& 4843	  & 1.1 & 1321	& 1316	& -0.4 \\\hline
 {\Small 473.astar}	  & 691	        & 754	& 9.1 & 0	& 0	& 0.0  & 359	& 363	  & 1.1 & 113	& 113	& 0.0  \\\hline
 {\Small 482.sphinx}	  & 1599	& 1693	& 5.9 & 11	& 9	& -18.2& 198	& 194	  & -2.0& 53	& 53	& 0.0  \\\hline
 {\Small 483.xalanc}	  & 9997	& 11453	& 14.6& 56	& 54	& -3.6 & 69534	& 68839	  & -1.0& 29875	& 29519	& -1.2 \\\hline
    \end{tabular}
  \end{center}
  \caption{Static metrics before (Base) and after \gcm{} (\GCM{}) on
    \SPEC{} at -Ofast. The \% Column show percentage increase in metric
    w.r.t. Base. \GCM{} improves LICM and inlining.}
  \label{tab:stats}
\end{table}
